Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-10-26 psy_peds_3.Rmd
update the saved outputs

```{r}
# estimate the counts
count_icd <- all_codes_desc %>%
  filter(date < end_date_plots &
         date >= start_date_plots ) %>%
    group_by( time_p ) %>%
  summarise(count_icd =  ifelse(n_distinct(patient_num) > obfuscation | isFALSE(obfuscation),
                               n_distinct(patient_num), 
                               0.5)) %>%
  mutate( period = ifelse( time_p < pandemic_start_date,
                           "before_pandemic",
                           "during_pandemic")
  )

# join the total with the disorder group count to estimate the percentage
perc_disorder_group <- count_icd %>%
  left_join(count_disorder_group, 
            by = c("time_p", "period")) %>% 
  replace_na(list(count_dg = 0))

>>>>

```{r}
# estimate the counts
count_icd_all <- all_codes_desc %>%
  filter(date < end_date_plots &
         date >= start_date_plots ) %>%
    group_by( time_p ) %>%
  summarise(count_icd =  ifelse(n_distinct(patient_num) > obfuscation | isFALSE(obfuscation),
                               n_distinct(patient_num), 
                               0.5)) %>%
  mutate( period = ifelse( time_p < pandemic_start_date,
                           "before_pandemic",
                           "during_pandemic")
  )

# join the total with the disorder group count to estimate the percentage
perc_disorder_group <- count_icd_all %>%
  left_join(count_disorder_group, 
            by = c("time_p", "period")) %>% 
  replace_na(list(count_dg = 0))
